Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-16 VMCAI-revised-version/final.tex
effectivity

%
\begin{theorem}\label{up-down}
{\sc Resilience}  is decidable for ideal-effective downward compatible WSTS with 
$\Safe=\downarrow \Safe$.
\end{theorem}

@@

\begin{theorem}\label{srp up down}
{\sc State-resilience},
{\sc Bounded-state-resilience} and
{\sc $k$-state-resilience}
are undecidable for strongly compatible WSTS with effective pred-basis
when
$\Safe=\uparrow \Safe$.
\end{theorem}

@@

The computability of $\uparrow \post^*(s)$ however seems a strong hypothesis. What are the WSTS for which $\uparrow \post^*(s)$ is computable for $s \in S$ ? \alain{One first answer is the class of effective downward-WSTS which are precisely effective $\post^*$-basis}. Moreover, 
\"Ozkan \cite{DBLP:conf/gg/Ozkan22} argues that it is precisely the WSTS for which the following problem is decidable.

>>>>

%
\begin{theorem}\label{up-down}
{\sc Resilience}  is decidable for ideal-effective downward-WSTS with 
$\Safe=\downarrow \Safe$.
\end{theorem}

@@

\begin{proposition}\label{srp up down}
{\sc State-resilience},
{\sc Bounded-state-resilience} and
{\sc $k$-state-resilience}
are undecidable for strongly compatible WSTS with effective pred-basis
when
$\Safe=\uparrow \Safe$.
\end{proposition}

@@

The computability of $\uparrow \post^*(s)$ however seems a strong hypothesis. What are the WSTS for which $\uparrow \post^*(s)$ is computable for $s \in S$ ? \alain{One first answer is the class of effective finitely branching downward-WSTS which are precisely effective $\post^*$-basis}. Moreover, 
\"Ozkan \cite{DBLP:conf/gg/Ozkan22} argues that it is precisely the WSTS for which the following problem is decidable.
